---
title: "ender-analysis"
output: html_document
date: "2024-12-17"
---

```{r setup, include=FALSE}
library(ggpubr)
library(broom)
library(car)
library(lme4)
library(lmerTest)
```

## Overall Scores Setup

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

```{r}
df <- read.csv("./out/study/scores_df.csv")
summary(df)
```

```{r}
# filter out pilots
# df <- subset(df, pilot == 0)
# are post test scores explained by being assigned to SA or SB?
# t.test(df[df$version == 'A', ]$score, df[df$version == 'B',]$score, alternative = "two.sided", var.equal = FALSE)
```


Test for equal variance using Levene's Test. Results show that there is no significant difference in variances between groups, so t-test is okay to use.
```{r}
# Set version as the group of the dataset
df$version <- as.factor(df$version)

# Remove outlier and pilot data
df <- subset(df, pilot == 0)
df <- subset(df, id != "rhino")

leveneTest(score ~ version, data = df)

leveneTest(pretest ~ version, data = df)

leveneTest(sus ~ version, data = df)
```

## T-test for Statistical Significance
```{r}
t.test(score ~ version, data = df, var.equal = TRUE, alternative = "greater")

t.test(score ~ version, data = df, var.equal = TRUE, alternative = "two.sided")
```

Check significance of version on pretest scores and SUS scores.
```{r}
t.test(pretest ~ version, data = df, var.equal = TRUE, alternative = "two.sided")

t.test(sus ~ version, data = df, var.equal = TRUE, alternative = "two.sided")
```

```{r}
# df <- read.csv("./out/study/combined3.csv")
# df <- subset(df, pilot == 0)
# df <- df[!grepl("^P", df$proof), ]
# summary(df)
```

## Per-question analysis
```{r}
df <- read.csv("./out/study/questionTypeData.csv")
summary(df)

# Set version as the group of the dataset
df$version <- as.factor(df$version)
df$questionType <- factor(df$questionType)

# Check variance for each questionType, all are not significant so equal variance is OK
#leveneTest(score ~ version, data = subset(df, questionType == 1))
#leveneTest(score ~ version, data = subset(df, questionType == 2))
#leveneTest(score ~ version, data = subset(df, questionType == 3))
#leveneTest(score ~ version, data = subset(df, questionType == 4))
#leveneTest(score ~ version, data = subset(df, questionType == 5))

leveneTest(score ~ version * questionType, data = df)
```
```{r}
lmm_model <- lmer(score ~ version * questionType + (1 | id), data = df)
summary(lmm_model)

# To check if version significantly affects the score for each questionType
anova(lmm_model)
```


```{r}

# Extract residuals
lmm_residuals <- residuals(lmm_model)

# Q-Q plot
qqnorm(lmm_residuals)
qqline(lmm_residuals, col = "red")
```

# Check significance of performance on individual questions
Check significance of performing better on "does this proof have a mistake?" questions
```{r}
t.test(score ~ version, data = subset(df, questionType==1), var.equal = TRUE, alternative = "two.sided")

# test significance of time taken
t.test(time ~ version, data = subset(df, questionType==1), var.equal = TRUE, alternative = "two.sided")
```
Check significance of performing better on "which step is wrong?" questions
```{r}
t.test(score ~ version, data = subset(df, questionType==2), var.equal = TRUE, alternative = "two.sided")

# test significance of time taken
t.test(time ~ version, data = subset(df, questionType==2), var.equal = TRUE, alternative = "two.sided")
```

Significance of "correct the proof" questions
```{r}
t.test(score ~ version, data = subset(df, questionType==3), var.equal = TRUE, alternative = "two.sided")

# test significance of time taken
t.test(time ~ version, data = subset(df, questionType==3), var.equal = TRUE, alternative = "two.sided")
```

Check significance of performing better on "must X be congruent to Y?" questions
```{r}
t.test(score ~ version, data = subset(df, questionType==4), var.equal = TRUE, alternative = "two.sided")

# test significance of time taken
t.test(time ~ version, data = subset(df, questionType==4), var.equal = TRUE, alternative = "two.sided")
```

Check significance of performing better on "is reason X correctly applied?" questions
```{r}
t.test(score ~ version, data = subset(df, questionType==5), var.equal = TRUE, alternative = "two.sided")

# test significance of time taken
t.test(time ~ version, data = subset(df, questionType==5), var.equal = TRUE, alternative = "two.sided")
```


Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
